---
title: "cross_ref_test2"
author: "Nicolás Molano Gonzalez"
date: "18 de Septiembre de 2018"
output: 
  html_document:
  fig_caption: true
---

```{r number_figures, echo=FALSE}
# This is a knitr hook to enable figure and table captions
# number figures
# from http://stackoverflow.com/a/18672268/1036500
library("knitr")
tn = local({
  i = 0
  function(x) {
    i <<- i + 1
    paste("<table><caption>", 'Figure ', i, ': ', x, "</caption><colgroup><col width='100'></col></colgroup><thead><tr class='header'></tr></thead><tbody></tbody></table><p>", sep = '')
  }
})
knit_hooks$set(fig.cap = function(before, options, envir) {
  if(!before)
    tn(options$fig.cap)
})
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$fig.cap) == F)  
    x
  else
    default_output_hook(x,options)
})

# number tables
# from http://stackoverflow.com/a/18672268/1036500
to = local({
  i = 0
  function(x) {
    i <<- i + 1
    paste("<table><caption>", 'Table ', i, ': ', x, "</caption><colgroup><col width='100'></col></colgroup><thead><tr class='header'></tr></thead><tbody></tbody></table><p>", sep = '')
  }
})
knit_hooks$set(tab.cap = function(before, options, envir) {
  if(!before)
    to(options$tab.cap)
})
default_output_hook = knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  if (is.null(options$tab.cap) == F)  
    x
  else
    default_output_hook(x,options)
})
```

```{r setup, echo=FALSE, message=FALSE}
library(pacman)
p_load(tidyverse)
p_load(knitr)
p_load(kfigr)
opts_chunk$set(message=FALSE, warning=FALSE)
```

# My document starts here

We can  embed plots, for example:

```{r first, anchor="figure", fig.cap="Rather small sample", fig.align='center',echo=F}
require(ggplot2)
qplot(rnorm(10), geom="histogram")
```

Note that for `r figr('first', TRUE, type="figure")` we can refer to the figure by the chunck label and that will generate an auto-numbered reference in the text that also links to the figure.

```{r second, anchor="figure", fig.cap="Look at this nice big sample", fig.align='center'}
require(ggplot2)
qplot(rnorm(1000), geom="histogram")
```

Note that for `r figr('second', TRUE, type="figure")` we can do the same thing, numbering is taken care of for us.

```{r mytable, anchor="table", tab.cap="my table about cars", tab.align='center'}
kable(mtcars)
```

And we can have a table, see `r figr('mytable', TRUE, type="table")` we can refer to the table with a numbered reference in the text that also links to the table.

We can refer to the figures and tables multiple times in the text with no problems: `r figr('first', TRUE, type="figure")`, `r figr('second', TRUE, type="figure")`, `r figr('mytable', TRUE, type="table")`